---
title       : Studying MPG for pairs for possible predictors
subtitle    : A shiny application
author      : Carlos L.  
job         : Data Sciences Specialization student
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [bootstrap,quiz, shiny, interactive]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}


--- 
### MOTIVATIONS

The mtcars set is database used in different stages of data sciences courses due to its simplicity and yet enough complexity to avoid trivial analysis.

The motivation of this shiny appliaction is to allow students to see different behaviors towards different pairs of predictors. 
Features:

* Full selection of first predictors and 2nd predictor restricted to discrete features.
* Exploratory plots, results of generalized linear model predictions in graph and in text

--- 
### APPLICATION INTERFACE

```{r opts.label = 'shiny'}
slidifyUI(pageWithSidebar(
  headerPanel("Studying Miles per Gallon for pairs for possible predictors"),
  sidebarPanel(
    selectInput('sel_predictor', 'Select first predictor', c('# of cylinders', 'Displacement(cu.in.)','Gross horsepower','Rear axle ratio','Weight','Quarter-mile time','V/S','Transmission','# forward gears','# carburetors')),
    radioButtons('colorBy', 'Coloring by the 2nd predictor',c('#Cylinder', 'VS','Transmission','# forward gears','# carburetors')
    ),
    h3("INSTRUCTIONS")
  ),
  mainPanel(
   tabsetPanel(
      tabPanel("MPG vs 2 predictors"),
      tabPanel("Predictions vs. Real values of MPG on GLM of 2 Predictors"),
      tabPanel("GLM Summary")
 
    )
  )
)
)
```

---

### FEATURES. PLOTS

```{r echo=FALSE,results='hide'}
data(mtcars)
mpgData <- data.frame(mtcars)
mpgData$am <- factor(mpgData$am,labels=c("Automatic","Manual"))
mpgData$cyl <- factor(mpgData$cyl)
mpgData$vs <- factor(mpgData$vs)
mpgData$gear <- factor(mpgData$gear)
mpgData$carb <- factor(mpgData$carb)
fit <- glm(mpg~cyl+am,data=mpgData,family="gaussian")
predvalues <- predict(fit,type="response")
predresults <- data.frame(MPG_PredVals=predvalues,MPG_RealVals=mpgData$mpg)

```

```{r echo=FALSE, fig.width=6,fig.height=3,fig.keep='all'}
layout(t(1:2))
ggplot(mpgData, aes_string(x="cyl", y="mpg",colour="am")) + geom_point()+ggtitle("MPG vs 2 predictors")
ggplot(predresults,aes(x=MPG_RealVals,y=MPG_PredVals))+ geom_point()+xlab("miles per gallon real values")+ylab("miles per gallon model predicted values")+ggtitle("Predictions vs. Real values of MPG on GLM of 2 Predictors")

```

* __MPG vs 2 predictors__: This feature shows the scatter plot mpg vs. the first predictor colored by the second predictor, so it is possible to explore possible groups and make a initial evaluation of the predictors
* __Predictions vs. Real values of MPG on GLM of 2 Predictors__: Our second feature shows the result of creating generalized linear model on the selected predictor. This is done by plotting predicted values of the data against the actual values.
* __GLM Summary__(next slide): It shows all the information about the generalized linear model of mpg from the 2 chosen predictors

---

```{r echo=FALSE,fig.height=1,fig.width=1}

print(summary(fit))

```
